Every day, we are surrounded by usage of ontologies. It is used in the background when we are on the World Wide Web at our computer or phone. Ontologies are in use everywhere. In this general introduction, there are chosen to examples where it can be useful to use an ontology. Both in the semantic web and in data integration, there could be huge set of data, so the domain of knowledge will then be large. Using ontologies to structuring the domain will be useful.

\subsection{Semantic Web}
The Semantic Web is a "web of data" that makes it easier for machines to understand the semantics of information on the World Wide Web. More precise it extends the network of human-readable web pages by including machine-readable metadata about pages and in which way the pages are related to each other, starting automated agents to access the Web smarter and perform tasks in place of the users. The term Semantic Web is also used specifically to refer to the format and technologies that activates it. The technologies that activates the semantic web process contain the "Resource Description Framework (RDF)", and notations such as RDF Schema and the Web Ontology Language, that all of them gives a formal description of concepts, terms and relationships within a given knowledge domain.\cite{website:wikipediasemanticweb}

The Web Ontology Language (OWL) is a knowledge representation language for authoring ontologies. OWL is approved by the W3C organization, and has getting academic, medical and commercial interest.

\subsection{Data integration}
Data integration includes combining data from different sources and give the user a view of those data. This process is widely used both commercial and in scientific purposes. In more and less all the information systems today, the data is coming from more than one data source. In web applications for example where a user can request a query variety  of information about cities such as weather forecast, hotels, car rentals and so on. To have all this information in one database, will duplicate the information. With data integration the solution can construct a virtual schema, to best model the answer the user want. Then the developers design adapters for each data source. The adapters just transform the local query request into  an an procesed form for the data-integration solution. \cite{website:wikipediadataintegration}

To make data integration possible in an easy way, it is very helpful to have standardized data. Standards defines the interface of a software system, for example standards define the syntax and semantics of a programming language or even a data model. Today, database systems are complex and are very often created of multiple independently parts that need to collaborate together. This is going to data integration where application often use multiple data sources. Standards that are developed by standards organizations or by industry groups are formal standards, but dominant products can be general accepted as a "de facto standards" without any formal standards process. \cite{database}

As mentioned in section 2, ontology is a model of a domain. The ontology is often used to make a model of the domain and then use the model to create a database. %UTDYP