The word ontology originally came from philosophy, and has been adopted in many other field of business. In the philosophical domain, the word ontology means a branch of metaphysics concerned with the study of existence.In the scientific and information "world" there are several definitions of the word ontology. Tom Gruber's definition: "An ontology is a specification of a conceptualization." or "Ontologies are specifications of a relational vocabulary". Wikipedia have these definition: "An ontology is a data model that represents a set of concepts within a domain and the relationships between those concepts".\cite{website:wikipediaontology} An ontology is aso a formal description of classes (sometimes called concepts) in a domain of discourse, each class has properties describing different features and attributes of the classes, and restriction on facets. There are a set of individual instances of classes that compose a knowledge base.\cite{website:standford} An ontology is developed or produced to set a structure of data for other programs to use.

In all these definitions for the same word, there are a lot of complex words like conceptualization, domain and 'relational vocabulary'. Conceptualization, we can say is an abstract, simplified picture of the world we want to be represented for some reason. A domain is a part of the world, like cats is a part of the pets world for example.

From this, an ontology is a detailed model of a part of the reality which is build up on the facts and relations that we know (knowledge domain). The W3C organization describe ontology: "An ontology defines the terms used to describe and represent an area of knowledge".\cite{website:whatontology}